---
title: First Post
author: Nick Bond
date: '2019-09-09'
slug: first-post
categories: []
tags:
  - R
  - dams
---

There's been recent suggestion that more dams should be built to safegaurd against future droughts. Setting aside the question of where a new dam would be built (most appropriate locations have been utilised already), the thing that often seems to be forgotten is that most of our dams are currently storing more air than water. So how many dams have we built in Australia? Here's a timline in R.

```{r}
library(tidyverse)
library(sf)
library(gganimate)
library(lubridate)
if(!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("dkahle/ggmap", force=TRUE)
library(ggmap)
```

```{R}

dams <-  readxl::read_excel("Dams-Australia-2010-v1.xls", sheet = "Australia") %>%
  janitor::clean_names() %>% slice(-c(1:2)) %>% unite("use", contains("purpose"), sep = ", ")

dams <- read_sf("kx-australian-dams-and-water-storages-SHP/australian-dams-and-water-storages.shp")
dams <- dams %>% mutate(DAM_DATE = ymd(DAM_DATE, truncated = 2)) %>% filter(!is.na(DAM_DATE))
dams <- cbind(dams, sf::st_coordinates(dams))
dams <- dams %>% arrange(DAM_DATE) %>%
  mutate(n_dams=row_number())

all_years <- data.frame(DAM_DATE = seq(from=min(dams$DAM_DATE, na.rm=TRUE), to=as.Date(cut(Sys.Date(), "year")), by="year"))
dams <- left_join(all_years, dams, by="DAM_DATE") %>% arrange(DAM_DATE) %>%
  mutate(Year = year(DAM_DATE)) %>% fill(DAM_DATE:n_dams)


library(ggmap)
oz_map <- get_map(location = 'Australia', zoom = 4, source = 'google', maptype="satellite")
n_years <- nrow(distinct(dams, Year))


dams_in_time <-
  ggmap(oz_map) +
  geom_point(data = dams, aes(x=X, y=Y, group = seq_along(Year), size = CAPACITY), colour = "red", alpha=0.5) +
  transition_reveal(Year, keep_last = TRUE) +
  labs(title = "Large Dams in Australia", 
       subtitle = 'Year: {frame_along},  Number of Dams: {dams$n_dams[dams$Year == frame_along][1]}',
       size = expression("Capacity (10"^3*"m"^3*")"))

dams_in_time <- animate(plot = dams_in_time, 
                        nframes = n_years, 
                        fps=2, 
                        device="png", 
                        height = 500, 
                        width =500, 
                        )



anim_save("oz_dams_in_time.gif")

```


```{r}
dams_in_time
```

